### 2011-01-11 trunk/IntroductionLetters/document.tex
finall version of the letters.

I would like to  investigate the possibility of continuing my PhD studies under
your supervision at the University of Calgary.  My name is Maha and I obtained
my Bsc and Msc in Computer Engineering from  Cairo University, Egypt in  2003
and 2009 respectively.  I worked both in the academic (as a Research Assistant)
and industrial (as a Software Engineer) sectors . I am planning to pursue a
research career by first continuing my Post Graduate studies. My main research
interest is in integrating software engineering methods
with different human-compture interaction.

Most my research experience is in Machine Learning but I have vast interest in
Software Engineering. I worked for four years as a Software Engineer for Engnet,
Egypt. After the first year, I was promoted to Team Leader and Senior Software
Engineer where I got more involved in software process and how to improve the
performance of developers. Since then, Software Engineering became my passion;
I took charge of improving the software development process,
helping developers for better collaborative work and looking for methods that will improve issue and bug tracking systems.
     I read  several  technical papers on software engineering, bug tracking,
     team collaboration and code analysis systems.  Because of my passion I
     decided to pursue my studies in PhD in Software Engineering field. (kindly
     see my CV for mor information.)

Currently, I work at Electronics Research Institute in the 'Signal and Image
Processing' research group. My work focuses on conducting research and related activities in the field of Machine learning and Image processing. I also work as a part time Research and Teaching Assistant in American University in Cairo (AUC).
  My research in AUC focuses on Arabic Handwriting Recognition especially improving interaction and recognition of Online Arabic handwriting systems.

 My research interests are in developing applications to improve
     interaction of tabletop surfaces and approachers for improving interactions
     between distributed agile teams. I am also intrested in how to help teams to create
     and maintain useful software but I am open to any idea in the field. I
     hope thes interests falls under your research interests as indicated in the web site of the Agile Software Engineering research group.

     I have preference towards studying in Canada where state of the art
     research exists and particularly in the University of Calgary due to its
     international recognition as one of the best Universities in Canada. I am
     wondering about the possibility of pursuing my graduate studies under your guidance and supervision at University of Calgary. I
write to seek your kind advice.

>>>>

I would like to investigate the possibility of continuing my PhD studies under your supervision at the University of Calgary. Since I wanted to pursue my PhD software Engineering, my friend"Dina Said" who is a graduate student in the department highly recommended you. I then talked with two of your students; "Maha Shouman" and "Ealaf Selim" who introduced me to the various research projects in the Agile group.

 My Name is Maha El Meseery and I obtained my Bsc and Msc in Computer Engineering from Cairo University, Egypt in 2003 and 2009 respectively. I worked both in the academic (as a Research Assistant) and industrial (as a Software Engineer) sectors. I am planning to pursue a research career by continuing my Post Graduate studies. My main research interest is integrating software engineering methods with different human-computer interaction.
.

Most of my research experience is in Machine Learning but I have a vast interest
in Software Engineering. I worked for four years as a Software Engineer for Engnet, Egypt. After the first year, I was promoted to Team Leader and Senior Software Engineer where I got more involved in software process and how to improve the performance of developers. Since then, Software Engineering became has become my passion; I took charge of improving the software development process, helping developers for better collaborative work and looking for methods that will improve issue and bug tracking systems. Because of my passion I decided to pursue my studies in PhD in Software Engineering field.

Currently, I am working at the Electronics Research Institute in the 'Signal and Image Processing' research group. My work focuses on conducting research and related activities in the field of Machine learning and Image processing with a focus on sketch recognition. I am also working as a part-time Research and Teaching Assistant in American University in Cairo (AUC). My research in AUC focuses on Arabic Handwriting Recognition especially improving interaction and recognition of Online Arabic handwriting systems.

My research interests are in mainly in the areas of developing applications to improve interaction of tabletop surfaces and approaches for improving interactions between distributed agile teams. Furthermore, I am interested in how to help teams to create and maintain useful software but I am also open to any idea in the field. I hope these interests falls under your research interests as indicated in the web site of the Agile Software Engineering research group.

I have preference towards studying in Canada and particularly in the University of Calgary due to its international recognition as one of the best Universities in Canada. I am wondering about the possibility of pursuing my graduate studies under your guidance and supervision at University of Calgary. I write to seek your kind advice.

Kindly find attached to the email my resume.

Maha
